From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-25 Pi+/paper/finite.tex
Lehmer Aut equiv example

When swapping two pairs of elements in positions "far-away", it does not matter
in which order the swapping happens, that is, we can slide the wires freely.

@@

The long form of the Coxeter relations are unwieldy and difficult to prove properties about by induction, and have
little connection to the broader scope of computational group theory. However, we can prove that the closures of the two
forms of the relations are equivalent, and work up to this equivalence!

@@

\jk{TODO an example here}
To remind ourselves, in a Lehmer code, the element $\el{r}$ at postition $k$ counts the number of inversions of the
element $\el{r}$. This corresponds exactly to what happens in the \cref{prop:fin-finexcept-3}. Looking at the operation
combinatorially, it is inserting element $\el{r}$ at the position $k$, meaning that it shifts the element
$k$places.\jk{needs rewriting after the example is here}

>>>>

When swapping two distinct pairs of elements (i.e. the indices of transpositions
differ by at least 1), it does not matter in which order the swapping happens,
that is, we can slide the wires freely.

@@

The modified form of the Coxeter relations are unwieldy and difficult to prove properties about by induction, and have
little connection to the broader scope of computational group theory. However, we can prove that the closures of the two
forms of the relations are equivalent, and work up to this equivalence!

@@

To see how the proof works combinatorically, let us go through an example. We will start from a following bijection $p: \Aut[\Fin[4]]$:
\begin{align*}
    p(0) \mapsto & 1 \\
    p(1) \mapsto & 3 \\
    p(2) \mapsto & 0 \\
    p(3) \mapsto & 2
\end{align*}

At first, we start from a full domain $\Fin[4]$ and full codomain $\Fin[4]$.
\[
    \begin{bmatrix}
        0 \\
        1 \\
        2 \\
        3
    \end{bmatrix}
    \mapsto
    \begin{bmatrix}
        0 \\
        1 \\
        2 \\
        3
    \end{bmatrix}
\]

As element $\el{0}$ is mapped to $\el{1}$, we remember that the last element of
result tuple is $1$. The appropriate elements on both sides are removed,
forming, respectively, $\FinExcept{4}[0]$ and $\FinExcept{4}[1]$. These are then
both transformed to $\Fin[3]$ using
\cref{prop:fin-finexcept}.~\ref{prop:fin-finexcept-2}, as shown below.
\[
    \begin{bmatrix}
        0 \\
        1 \\
        2
    \end{bmatrix}
    \equiv
    \begin{bmatrix}
        1 \\
        2 \\
        3
    \end{bmatrix}
    \mapsto
    \begin{bmatrix}
        0 \\
        2 \\
        3
    \end{bmatrix}
    \equiv
    \begin{bmatrix}
        0 \\
        1 \\
        2
    \end{bmatrix}
\]

Then, the original permutation specified that the element $\el{1}$ has to be
mapped to $\el{3}$. Since we performed renumbering, now it means that element is
mapped to $\el{2}$ - the resulting tuple now looks like $[2, 1]$. We yet again remove these from the domain and codomain,
forming $\FinExcept{0}[0]$ and $\FinExcept{0}[2]$.

\[
    \begin{bmatrix}
        0 \\
        1
    \end{bmatrix}
    \equiv
    \begin{bmatrix}
        1 \\
        2
    \end{bmatrix}
    \mapsto
    \begin{bmatrix}
        0 \\
        2
    \end{bmatrix}
    \equiv
    \begin{bmatrix}
        0 \\
        1
    \end{bmatrix}
\]

The situation repeats two more times: first, by assinging $\el{0}$ to $\el{1}$,
giving the tuple $[0, 2, 1]$ and transforming the domain and codomain:
\[
    \begin{bmatrix}
        0
    \end{bmatrix}
    \equiv
    \begin{bmatrix}
        1
    \end{bmatrix}
    \mapsto
    \begin{bmatrix}
        0
    \end{bmatrix}
    \equiv
    \begin{bmatrix}
        0
    \end{bmatrix}
\]

And finally, by assinging $\el{0}$ to $\el{0}$, forming a tuple $[0, 0, 2, 1]$ and

At this point we see that the renumbering of the domain is done in an orderly
way (always shifting by 1), so it can be ignored. On the other hand, the
ordering of the codomain is what matters. Each time we remove an element, all
larger elemens are in effect decreased by one.

To remind ourselves, when we introduced the combinatorial interpretation of
Lehmer codes, the element $\el{r}$ at postition $k$ was said to count the number
of inversions of the element $\el{r}$. Thus, this is exactly the meachanism in
which the induction step works.

This corresponds exactly to what happens in
the \cref{prop:fin-finexcept-3}. Looking at the operation combinatorially, it is
inserting element $\el{r}$ at the position $k$, meaning that it shifts the
element $k$places.\jk{needs rewriting after the example is here}

Viewing the codomain as a vector of four elements, element $\el{0}$ has zero
inverses, element $\el{1}$ has 1 inverse, element $\el{2}$ has 1 inverse, and
element $3$ has
